---
title: "assignment writeup"
output: html_document
---
#Summary
This project aims to predict how well people perform weight lifting activities using the Weight Lifting Exercises Dataset (http://groupware.les.inf.puc-rio.br/har).
```{r}
library(caret)
```

Load data.
```{r}
trainDat = read.csv("pml-training.csv")
testDat = read.csv("pml-testing.csv")
```
Remove columns with missing data.
```{r}
trainDat_clean = trainDat[, which(colSums(is.na(trainDat)) == 0 & colSums(is.na(testDat)) == 0)]
testDat_clean = testDat[, which(colSums(is.na(trainDat)) == 0 & colSums(is.na(testDat)) == 0)]
```
Train random forest model with 5-fold crossvalidation. I chose random forest because it has good general performance and can handle hetergeneous independent variables and multiple categories in the dependent variable.
```{r}
train_control <- trainControl(method="cv", number=5)
model_rf <- train(classe ~., data=trainDat_clean[, c(2:ncol(trainDat_clean))], trControl=train_control, method="rf")
print(model_rf)
```
The expected out of sample error is 1 - 0.9994904 = 0.0005096.

Prediction results for 20 different test cases.
```{r}
testDat_pred = predict(model_rf, testDat_clean[, c(2:ncol(trainDat_clean))])
testDat_pred
```

